Constraint result to the self-interacting dark matter model without dark energy in cosmology

### 2025-04-16 article/article.tex
use the times roman format for some figures

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccc}
         \hline\hline
         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
         \hline
         BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
         LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
         LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
         LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
         ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
         QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
         Lya & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
         \hline
         LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
         ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
         \hline
      \end{tabular}
      \caption{The BAO dataset from DESI DR2.}
      \label{tab:3}
   \end{table*}

@@

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_2.pdf}
      }
      \caption{The constraint result from the OHD + SNe Ia data.}
   \end{figure}

@@

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_2.pdf}
      }
      \caption{The constraint result from the OHD + SNe Ia + BAO data.}
      \label{fig:5}
   \end{figure}

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccccc}
         \hline\hline
         Model 1 & OHD & SNe Ia & SNe Ia + QSO 
         & OHD + SNe Ia & BAO & OHD + SNe Ia + BAO \\
         \hline
         $\Omega_{2,0}$ & $0.324_{-0.066}^{+0.056}$ & $0.380_{-0.020}^{+0.020}$
          & $0.378_{-0.020}^{+0.020}$ & $0.375_{-0.019}^{+0.019}$
          & $0.298_{-0.007}^{+0.007}$ & $0.308_{-0.007}^{+0.005}$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.08$ & $<-2.73$ & $<-2.75$
         & $<-2.91$ & $<-3.38$  & $<-3.71$ \\
         $\log_{10}(M_x/$GeV) & $>-9.85$ & $>-9.26$ & $>-9.23$
         & $>-9.13$ & $>-8.56$ & $>-8.26$ \\
         \hline
      \end{tabular}
      \caption{The constraint results of Model 1.}
      \label{tab:5}
   \end{table*}

@@

@@

   Apply the Eq.(\ref{eq:12}) to Eq.(\ref{eq:8}), we can get a simple nonlinear
   second-order differential equation for the redshift $z(t)$, which can
   be written as \begin{equation}
      2H_0^2\Omega_{1,0}(1+z)^2z'z''+\kappa C_1z'{}^4-5H_0^2\Omega_{1,0}(1+z)z'{}^3
      +3H_0^4\Omega_{1,0}^2(1+z)^3z'-H_0^4\Omega_{1,0}^2\kappa C_1[(z+1)^4-1]
      =H_0^4\Omega_{1,0}^2\kappa C_1,
   \end{equation}
   where the prime denotes the derivative with respect to $t$.
   The equation can be simplified as
   \begin{equation}
      2H_0^2\Omega_{1,0}y^2y'y''+\kappa C_1y'{}^4-5H_0^2\Omega_{1,0}yy'{}^3
      +3H_0^4\Omega_{1,0}^2y^3y'-H_0^4\Omega_{1,0}^2\kappa C_1y^4=0,
   \end{equation}
   where $y=z+1$, now it is a homogeneous function and we can give the
   general solution as $y=\exp{f}$ with $f$ a function of $t$, the equation
   now is \begin{equation}
      2H_0^2\Omega_{1,0}f'f''+\kappa C_1f'{}^4-3H_0^2\Omega_{1,0}f'{}^3
      +3H_0^4\Omega_{1,0}^2f'-H_0^4\Omega_{1,0}^2\kappa C_1=0.
   \end{equation}
   We use $g=f'$, which also gives $g(t)=y'/y=-H(t)$, then the equation can be written as
   \begin{equation}
      2H_0^2\Omega_{1,0}gg'+\kappa C_1g^4-3H_0^2\Omega_{1,0}g^3
      +3H_0^4\Omega_{1,0}^2g-H_0^4\Omega_{1,0}^2\kappa C_1=0.
   \end{equation}
   It can be theoretically solved and the solution is like
   \begin{equation}
      g(t)=\mathcal{G}\left(-\frac{t}{2H_0^2\Omega_{1,0}}+Const\right),
   \end{equation}
   where $\mathcal{G}$ is the inverse function of
   \begin{equation}
      \mathcal{F}(x)=\frac{3H_0\sqrt{\Omega_{1,0}}\mathrm{arctanh}\frac{x}{H_0\sqrt{\Omega_{1,0}}}
      -\kappa C_1\log(x^2-H_0^2\Omega_{1,0})+\kappa C_1\log(\kappa C_1x^2-3H_0^2\Omega_{1,0}x
      +H_0^2\Omega_{1,0}\kappa C_1)}{9H_0^4\Omega_{1,0}^2-4H_0^2\Omega_{1,0}(\kappa C_1)^2}.
   \end{equation}
   In this term, $\displaystyle\mathrm{arctanh}(x)\doteq \frac{1}{2}\log\left(\frac{x+1}{x-1}\right)$
   when $x<-1$, and the $Const$ is determined by the boundary condition $g(0)\to -\infty$, which is

>>>>

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccc}
         \hline\hline
         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
         \hline
         BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
         LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
         LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
         LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
         ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
         QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
         Ly$\alpha$ & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
         \hline
         LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
         ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
         \hline
      \end{tabular}
      \caption{The BAO dataset from DESI DR2.}
      \label{tab:3}
   \end{table*}

@@

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_2.pdf}
      }
      \caption{The constraint result from the SNe Ia + OHD data.}
   \end{figure}

@@

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_2.pdf}
      }
      \caption{The constraint result from the BAO + SNe Ia + OHD data.}
      \label{fig:5}
   \end{figure}

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccccc}
         \hline\hline
         Model 1 & OHD & SNe Ia & SNe Ia + QSO 
         & SNe Ia + OHD & BAO & BAO + SNe Ia + OHD \\
         \hline
         $\Omega_{2,0}$ & $0.324_{-0.066}^{+0.056}$ & $0.380_{-0.020}^{+0.020}$
          & $0.378_{-0.020}^{+0.020}$ & $0.375_{-0.019}^{+0.019}$
          & $0.298_{-0.007}^{+0.007}$ & $0.308_{-0.007}^{+0.005}$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.08$ & $<-2.73$ & $<-2.75$
         & $<-2.91$ & $<-3.38$  & $<-3.71$ \\
         $\log_{10}(M_x/$GeV) & $>-9.85$ & $>-9.26$ & $>-9.23$
         & $>-9.13$ & $>-8.56$ & $>-8.26$ \\
         \hline
      \end{tabular}
      \caption{The constraint results of Model 1.}
      \label{tab:5}
   \end{table*}

@@

   Fig \ref{fig:6} shows the difference between classical dataset ($H(z)$, SNe Ia)
   and newly released BAO dataset. The BAO dataset gives a strict constraint to
   $\Omega_{2,0} \simeq 0.3$, lower than the SNe Ia dataset about $3\sigma$, which
   gives a higher value $\Omega_{2,0} \simeq 0.4$. The constraint result to Pantheon+
   SNe Ia dataset in $\Lambda$CDM model is $\Omega_M \simeq 0.33$ (\cite{Borghi_2022}),

@@

   Apply the Eq.(\ref{eq:12}) to Eq.(\ref{eq:8}), we can get a simple nonlinear
   second-order differential equation for the redshift $z(t)$, which can
   be written as \begin{equation}
      2H_0^2\Omega_{1,0}(1+z)^2z'z''+\kappa C_1z'{}^4-5H_0^2\Omega_{1,0}(1+z)z'{}^3
      +3H_0^4\Omega_{1,0}^2(1+z)^3z'-H_0^4\Omega_{1,0}^2\kappa C_1[(z+1)^4-1]
      =H_0^4\Omega_{1,0}^2\kappa C_1,
   \end{equation}
   where the prime denotes the derivative with respect to $t$.
   The equation can be simplified as
   \begin{equation}
      2H_0^2\Omega_{1,0}y^2y'y''+\kappa C_1y'{}^4-5H_0^2\Omega_{1,0}yy'{}^3
      +3H_0^4\Omega_{1,0}^2y^3y'-H_0^4\Omega_{1,0}^2\kappa C_1y^4=0,
   \end{equation}
   where $y=z+1$, now it is a homogeneous function and we can give the
   general solution as $y=\exp{f}$ with $f$ a function of $t$, the equation
   now is \begin{equation}
      2H_0^2\Omega_{1,0}f'f''+\kappa C_1f'{}^4-3H_0^2\Omega_{1,0}f'{}^3
      +3H_0^4\Omega_{1,0}^2f'-H_0^4\Omega_{1,0}^2\kappa C_1=0.
   \end{equation}
   We use $g=f'$, which also gives $g(t)=y'/y=-H(t)$, then the equation can be written as
   \begin{equation}
      2H_0^2\Omega_{1,0}gg'+\kappa C_1g^4-3H_0^2\Omega_{1,0}g^3
      +3H_0^4\Omega_{1,0}^2g-H_0^4\Omega_{1,0}^2\kappa C_1=0.
   \end{equation}
   It can be theoretically solved and the solution has a form like
   \begin{equation}
      g(t)=\mathcal{G}\left(-\frac{t}{2H_0^2\Omega_{1,0}}+Const\right),
   \end{equation}
   where $\mathcal{G}$ is the inverse function of
   \begin{equation}
      \mathcal{F}(x)=\frac{3H_0\sqrt{\Omega_{1,0}}\mathrm{arctanh}\frac{x}{H_0\sqrt{\Omega_{1,0}}}
      -\kappa C_1\log(x^2-H_0^2\Omega_{1,0})+\kappa C_1\log(\kappa C_1x^2-3H_0^2\Omega_{1,0}x
      +H_0^2\Omega_{1,0}\kappa C_1)}{9H_0^4\Omega_{1,0}^2-4H_0^2\Omega_{1,0}(\kappa C_1)^2}.
   \end{equation}
   In this term, $\displaystyle\mathrm{arctanh}(x)\doteq \frac{1}{2}\log\left(\frac{x+1}{x-1}\right)$
   when $x<-1$, and the $Const$ is determined by the boundary condition $g(0)\to -\infty$, which is
